Global adjoint tomography -- Model GLAD-M25

### 2018-10-18 main.tex
Updates from ShareLaTeX

\section{Starting Model GLAD-M15}

As the continuation of our previous work, we used GLAD-M15 as our
starting model\citep{bozdaug2016global}.
The GLAD-M15 is a 3D transversely isotropic earth model. Its uses
GLAD-M00, a combined 3-D mantle model S362ANI \citep{kustowski2008anisotropic}
with 3-D crust model CRUST2.0 \citep{bassin2000current}, as its own starting model.
Instead of relying to the "crust correction", SPECFEM mesher enables us to incorporate
the 3D crustal model so we are able to update the crust and mantle structures at same
time with any trade-off. Besides, the.

GLAD-M15, same as  S362ANI, provides 6 model parameters, mass density($\rho$), two compressional
wavespeeds($\alpha_v$ and $\alpha_h$), two shear wavespeeds($\beta_v$
and $\beta_h$) and a dimenionless parameter($\eta$). We will discuss
the model parametrization in detail in the following sections.

GLAD-M15 then uses 256 earthquakes and broad-band seismic data to do the 3D full-waveform
inversion\citep{bozdaug2016global}. The first 12 iterations of GLAD-M15 was
performed under 27 secs and the last 3 under 17 secs. We will keep our model
resolution as 17s in our model. As shown in our later analysis,
GLAD-M15 proven good enough improvements over S362ANI in both our inversion
dataset and held-out test dataset. It also shows both significant misfit reduction
in all measurement categories and and better behavior in statistic analysis from distribution
of the phase measurements, which will discussed in the following sections.

\section{Earthquakes}

In addition to the 256 earthquakes used in the first generation model GLAD-M15, we
carefully picked 784 more earthquakes from Global Centroid-Moment-Tensor catalog\citep{}
and added them into our database, making the total number of earthquakes reach 1,040.
The lower band of moment magnitude, is set at 5.5 to ensure the signal-to-noise ratio at
the global scale. The upper bound of magnitude is set at 7.2 and duration of earthquakes
is set at 9 sec since we can use point representation and Gaussian-type source
time function.
We also constrain the duration of CMT sources to be smaller than 17s.
The locations of 1040 earthquakes is shown in fig.\ref{fig:source_correction}a.

To ensure a even global coverage, we used the seismic stations mainly from several global
seismic networks such as Global Seismic Network(II, IU, IC, US, CU and GT),
GEOFON(GE), GEOSCOPE(G), and regional networks, such as MedNet(MN),
, Brazilian Lithospheric Seismic Project(BL), Chilean National Seismic Network(C), Japan Meteorological
Agency Seismic Network(JP) and etc. The number of seismic stations usually ranges
from 150 to 500, depending on the availability of seismic stations when the earthquake
happened. The distribution of seismic stations is in Fig.\ref{fig:source_correction}b and
data is download from the Incorporated Research Institutions for Seismology(IRIS).

We use the source inversion algorithm of \cite{liu2004spectral}. This algorithm set the
target misfit function as the normalized waveform difference and envelope difference between
observed data, \textbf{d} and synthetic data generated from GLAD-M15, \textbf{s}.

\begin{multline}
  \chi = \sum\limits_{c=1}^{N_c} \omega_c \sum\limits_{r=1}^{N_r} \omega_{cr}
       \sum\limits_{m=1}^{N_m} \omega_{crm}
       \Big\{ \lambda {\frac
              { \int \big[ \mathbf{d}_m(t) - \mathbf{s}_m(t - \Delta t, \mathbf{m}_{15}) \big]^2 dt }
              {\int \big[ \mathbf{d}_m(t) \big]^2  dt } }\\
         + (1 - \lambda) \frac
              {\int \big[ e(\mathbf{d}_m(t)) - e(\mathbf{s}_m(t - \Delta t, \mathbf{m}_{15})) \big]^2 dt }
              {\int \big[ e(\mathbf{d}_m(t)) \big]^2  dt} \Big\}
\end{multline}

Following \cite{ekstrom2012global}, seismograms were filtered into 50-100s
to select 3-component body wave windows and 60-100s to select 3-component
surface wave windows. Thus, the number of measurements categories $N_c$,
is 6. To balance the contribution from each category, the weighting for each
category $\omega_c$, is the reciprocal of the number of measurements in that
category. The $N_r$ is the number of seismic stations in one category. $\omega_r$
is the receiver weighting assigned to each individual stations, which we will discuss
that in detail in the following sections. $N_m$ is the number of measurements for one
seismic stations in one measurements category and $\omega_m$ is the measurements weightings
, which is simply set to 1. The inverted parameters includes moment tensors, longitude,
latitude and depth. In order to get the frechet derivatives for each parameter, there is
one global-scale forward simulation needed to be done so the source inversion becomes a very expensive
operation.

Since we shifted the synthetic data based on the cross-correlation to its correspond observed
data to the best match of the pair, our source inversion is not very sensitive to
the origin time of earthquakes. In addition to prepare the future Q inversion,
A grid search for the origin time and scalar moment correction was introduced
directly to future calibrate the sources afterwards following \cite{zhu2012structure}.
The grid-search calibration has a linear effect on the seismograms so it doesn't take extra
simulation time.

Fig.\ref{fig:source_correction} shows the source correction results.
Most of the earthquakes shows a shallower depth after the source inversion
(Fig.\ref{fig:source_correction}b and Fig.\ref{fig:source_correction}c),
in consistent with \cite{hjorleifsdottir2010effects}.
We observed $-2.62\pm2.49$km depth change compared with the global CMT solutions.
The scalar moment, on the average, has $5.31\pm3.91$\% change and change of origin time
is $-0.60\pm1.17$ sec.

Starting from GLAD-M22, we added extra 440 earthquakes from GLobal CMT catalog,
mainly in previously poorly covered regions. However, due to computational cost,
we didn't implement the 1st stage source inversion in the newly added 440
earthquakes but only calibrate its origin time and scalar moment.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/events_1480.pdf}
  \caption{1480 earthquakes used in this study. (a) Distribution of earthquakes. Colors of beach balls indicate the depth range of earthquakes from Global CMT Catalog \citep{ekstrom2012global}. {\textbf{\color{Blue} Blue}} is for shallow earthquakes above 50km, \textbf{{\color{ForestGreen} Green}} is between 50 and 300km and \textbf{{\color{Red} Red}} is below 300km. (b) and (c) Histograms of earthquake moment magnitudes and depths.}
  \label{fig:event_1480}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
  \caption{Source correction results for 1040 events used in the inversion. (a) Map views of depth changes. (b) Distribution of seismographic stations used in the source inversion stage.(c) depth change of CMT sources compared to its initial solution from the Global CMT Catalog. (d)-(f) Histograms of depth, origin time and scalar moment changes.}
  \label{fig:source_correction}
\end{figure}

\section{Seismic Data}

Seismic stations have been very carefully picked to ensure global coverage and high data quality.
Other than the networks we mentioned in the source inversion, we include all the data we can
downloaded from IRIS data center. Regional and temporary networks has become a significant part
in our database and greatly improve the ray coverage at specific regions, such as US Array(TA),
Africa Array(AF), Canadian National Seismograph Network (CN), Geoscience Australia (AU),
Brazilian Lithospheric Seismic Project (BL),
Antarctic Seismographic Argentinean Italian Network (AI),
the New Zealand National Seismograph Network (NZ) and etc.

The data, associated with the earthquakes, was downloaded from several data centers,
including IRIS, ORFEUS, INGV, IPGP, ETH, GEONET and etc.
There are in total of 275 seismic networks (with individual network code) and 11,800
seismic stations used in the structural inversion stage. Fig.\ref{fig:stations}
shows the distribution of seismic stations.

\begin{figure}
  \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
  \caption{Distribution of 11,800 seismographic stations on the globe. Colors denote the number of events which they contribute waveforms to in the model inversion stage. Stations with event response < 400 are plotted in smaller size and they are usually temporary arrays which are deployed over a short period of time. The max event response comes from IU.ANMO, which contribute ed to 1442 out of 1480 earthquakes in out dataset.}
  \label{fig:stations}
  \centering
\end{figure}

\section{Misfit function and Model Parametrization}

This sections will discuss how we define the the misfit function and how we parameterize the model.
The overall misfit, $\Phi$, is defined as follows:

\begin{align}
\label{eq:misfit}
\Phi = \sum_{s}^{S} \omega_s \sum_{c}^{C} \omega_{c} \sum_{r}^{R_{sc}} \omega_{scr} \sum_{w}^{N_{scr}} \omega_{scrw}\, \chi_{scrw}
\quad ,
\end{align}\\
where~$S$ denotes the number of sources, $C$ the number of categories,
$R_{sc}$ the number of receivers for source~$s$ and category~$c$,
and~$N_{scr}$ the number of measurements for source~$s$, category~$c$
and receiver~$r$.

The misfit for source~$s$, category~$c$, receiver~$r$, and window~$w$ is
\begin{align}
  \chi_{scrw} = \int \Big[ \frac {\Delta \tau_{scrw}} {\sigma_{scrw}} \Big]^2 d\omega
\quad ,
\end{align}
is a frequency-dependent phase measurements using then multi-taper technique.
where $\Delta m_{scrw}$ denotes a measurement with associated standard deviation~$\sigma_{scrw}$.-

\subsection{Weightings}
Weighting is crucial to the global tomography to compensate the uneven distribution
of earthquakes and seismic stations. First, most of the earthquakes happen in the
in the plate boundaries. There are also several seismic active zones, such as Japan,
Fiji Tonga and South America, where there are a lot of earthquakes clustered near
the subduction slabs.
Second, most of the seismic stations located in the continents, especially located in
the northern hemisphere. Besides, there are quite a few dense seismic arrays,
for example US array, deployed recently, which has hundred or thousands of instrument deployed
at the regional scale, which will has a very strong footprint on the misfit gradients if no weighting
been applied.

All the factors mentioned above will lead to a uneven distribution of
ray paths and thus uneven sampling of the earth structure. Our weighting strategy
is developed to compensate such effects. There are two terms in the misfit function
receiver weightings, $\omega_{scr}$, and source weightings $\omega_{s}$.
The calculation of both terms can be abstracted as: given the distribution of
points determine the weighting associated with each point.
Here we introduce the exponential weightings to describe the density of points and
determine the point weightings. Given a set of points $p_i$, the distance between
two is $r_{ij}$, the weightings associated with each point, $w_i$, could be obtained by:

\begin{equation}
w_{i} = \frac{1}{A} \left(
  \sum_{j=1}^N \exp \left[ \mbox{} - \left( \frac{r_{ij}} {r_{0}} \right)^2 \right] \right) ^{-1}
\label{eq:spatial_weights}
\end{equation}
where $r_{0}$ is the sensitivity distance and $A$ is the normalization term.
The reference distance $r_0$ will control ratios of weightings between dense and
sparse regions. For more details for the weightings, please refer to the Appendix XXX.

\subsection{Model Parametrization}
Transversely isotropy model parametrization is used in our model, same as S362ANI(GLAD-M00)
and GLAD-M15. Comparing to a general anisotropic model which has 21 independent variables,
our model could be described by 5 Love parameters, A, C, L, N and F\citep{love2013treatise}.
Since it is more straight forward to use  wavespeed as model parameters in seismology,
we choose $\alpha_v$, $\alpha_h$, $\beta_v$, $\beta_h$ and $\eta$.
Assuming the radial anisotropy is due to shear anisotropy, these 5 parameters
can be further reduced to 4, we introduced the bulk sound speed,
$c=\sqrt{\kappa/\rho}$. Our final parameters are:\\
\begin{align*}
      c &= \sqrt{\kappa/\rho} \\
\beta_v &= \sqrt{L/\rho} \\
\beta_h &= \sqrt{N/\rho} \\
\eta & = F/(A-2L)
\end{align*}

Since density is hard to constrain due to the period band we are working on, the $\rho$ kernel is obtained by scaling the isotropic shear wavespeed kernel\citep{montagner1989petrological},\\
\begin{equation*}
    \delta ln\rho = 0.33\delta ln\beta
\end{equation*}

where $\beta$ is defined as the Voigt average of the radially anisotropic shear wave speeds\citep{babuska1991seismic}
$$\beta = \sqrt{(2\beta_v^2 + \beta_h)/3}$$

Based on the parametrization described above, the perturbations in misfit functions would be:

\begin{equation*}
    \delta \chi = \int_V
      (K_c\delta lnc + K_{\beta_v}\delta ln\beta_v + K_{\beta_h}\delta ln\beta_h +
      K_\eta \delta ln\eta) dV
\end{equation*}

\section{Adjoint Tomography Workflow}

The flow chart for adjoint tomography is shown in Fig.\ref{fig:adjoint_workflow}.
The workflow starts with a certain number of earthquakes. Here, we used the
inverted CMT sources from the Global CMT catalog. Based on the time
of earthquakes, we downloaded observed data, including time series and StationXML,
from IRIS and other data centers. The we convert the sources, StationXML and time series
into ASDF files. Each ASDF file usually contains a complete set of data from one
earthquake. The data download and conversion need to be done only once. The raw observed data,
storing in ASDF, could be reused afterwards.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.pdf}
  \caption{Adjoint Tomography Workflow.}
  \label{fig:adjoint_workflow}
\end{figure}

\subsection{Forward simulation}

The forward simulation takes the CMT sources, stations and Earth models as input.
We will first generate mesh based on the models. The CMT sources and station will
be fed into the solver to generate synthetic seismograms and forward wavefield snapshots.
SEPCFEM3D\_GLOBE with GPU acceleration is used on Titan at the Oak Ridge Nation Lab for
both mesher and solver part.

To simulate 120min of seismograms at 17sec resolution, it takes 384 Tesla K20X
GPUs approximately 10 mins to run on Titan. To precisely calculate the sensitivity
kernels, there is forward wavefield saved to the disk and those will used in the
adjoint simulation in the later stage. In the current resolution
and simulation length, the forward wavefield saved is above 1 terabytes
for each earthquake. Given the size the 1480 earthquakes, we have 1.5 petabytes of
wavefield saved to disk using ADIOS\citep{liu2014hello} during about 10 hours
of simulation using 15,360 GPUs.
It is huge volume of data saved to disk in a relatively short period of time, in which case
ADIOS really helped to relief the I/O bottleneck.

\subsection{Seismic Data Processing}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.pdf}
  \caption{Preprocessing Workflow for seismic data.}
  \label{fig:preprocess_workflow}
\end{figure}

The seismic data processing takes the raw observed and synthetic data as input,
and generate s the adjoint sources as the output. As shown
in Fig.\ref{fig:preprocess_workflow}, preprocessing includes:
\begin{enumerate}
  \item Signal processing that remove the instrument response from observed data
    to recover the true ground motion. Both observed and synthetic data will be
    filtered into a certain period band. Then the two horizontal components of the
    seismograms are rotated from North, East to radial and transverse only if the
    StationXML passed the sanity check.
  \item Window selection that picks the time window on a pair of
    observed and synthetic seismograms. Pyflex(python version
    of FLEXWIN\citep{maggi2009automated}), is
    such a tool that automatically generate windows where observed data and
    synthetic data are close enough to make measurements based on user defined
    criteria.
  \item Multi-taper measurement that generates frequency-dependent travel-time
    difference within the windows selected from the last step.
    The output files contains both the measurements and misfit values.
  \item Window cleaning that get rid of bad windows(and associated
    measurements), only keeping good ones based on the statistical analysis of
    measurements.
  \item calculate the adjoint sources with the sorted windows.
  \item For each window and associated measurement, calculate its weightings
    that will be applied at the summation stage and calibrate its contribution
    into the overall misfit function, using the method we mentioned before.
  \item Construct the final adjoint sources by summing the adjoint source from
    different windows and measurement categories.
\end{enumerate}

Even though it is such a computational demanding process as the forward and adjoint
simulation, only taking about $1\%$ CPU hours in the whole workflow, it is crucial
that directly impact the inversion results. It decides which measurement
will be taken into consideration and have a footprint in the final gradient.
We are very careful at this stage, including a lot of checks, such as the Station and
response integrity check, and also filtering out bad measurements to avoid big outliers.
On the other hand, it is very process-demanding, which means it has complex data and
control flows, that every seismograms will go through quite a few of processes
before the final results is generated. We have millions of seismic traces and ten
millions of windows, it is impossible to human-check every trace and measurements.
I will go into more depth about this part in the following sections, discussing our
efforts how to make the data and process safe and robust.

\subsection{Adjoint Simulation}

The adjoint simulation takes the adjoint sources as input, and calculate the frechet
derivatives as output. The computation cost is about twice as the forward simulation since
it is both calculating the adjoint wavefiled and reconstruct the forward wavefield.
Other than the adjoint sources, the adjoint simulation also reads in the saved forward
wave, to fully incorporate attenuation and more exactly calculate the anelastic
sensitivity kernels.
After the adjoint simulation is done, the save wavefield could be deleted and disk
space would be freed.
One Adjoint simulation takes about 25 mins for 17sec resolution for 120min simulation
at 17s resolution.

\subsection{Post-processing}

>>>>

\section{Starting model GLAD-M15}

As a continuation of our previous work~\citep{bozdaug2016global},
we used ``first generation'' model GLAD-M15 as our
starting model.
GLAD-M15 is a 3D transversely isotropic earth model, which combined
3D mantle model S362ANI~\citep{kustowski2008anisotropic}
with 3D crustal model CRUST2.0~\citep{bassin2000current} as its starting model.
In this study,
we continue to use the same transversely isotropic model parametrization.
Instead of relying on ubiquitous ``crustal corrections'',
the mesh implementation of the crust in the spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02b,PeKoLuMaLeCaLeMaLiBlNiBaTr11} enables us accurately accommodate topography and bathymetry as well as variations in the Moho.
GLAD-M15 was constructed using a global data base of 256 earthquakes.
The first 12 iterations of the GLAD-M15 inversion used three-component seismograms with a shortest period of 27~s,
and the final 3 iterations reduced this further to 17~s.
In this study we also used three-component seismograms with a shortest period of 17~s.

\section{Earthquakes}
\label{section:earthquakes}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/source_corrections.pdf}
  \caption{Source corrections for 1,040 out of 1,480 events used in the structural inversion. (a) Map view of depth changes. (b) Distribution of seismographic stations used for source inversions. (c) Depth change relative to the original global CMT Catalog depth. (d)--(f) Histograms of depth, origin time, and scalar moment changes relative to the CMT Catalog.
  {\color{red} Wenjie: please put a space between ``depth'' and ``km'' in the x-axis labels of figures C and D.}
  }
  \label{fig:source_correction}
\end{figure}

In addition to the 256 earthquakes used for the construction of first generation model GLAD-M15, we initially selected 784 carefully chosen additional earthquakes from the global Centroid-Moment Tensor (CMT) catalog~\citep[e.g.,][]{Ekstrom12},
and added them to our database, resulting in a total number of 1,040 earthquakes.
To ensure a good signal-to-noise ratio on a global scale,
the smallest moment magnitude in the database is set to~5.5,
and to avoid complications associated with source size,
the largest moment magnitude is set to~7.2.

Before using the 1,040 earthquakes in our structural inversion,
we performed CMT inversions in model GLAD-M15,
the results of which are summarized in Fig.~\ref{fig:source_correction}.
To ensure even global coverage,
we used seismographic stations from the  Global Seismic Network (II, IU, IC, US, CU, and GT),
GEOFON~(GE), GEOSCOPE~(G), and several regional networks, such as MedNet~(MN),
the Brazilian Lithospheric Seismic Project~(BL), the Chilean National Seismic Network~(C),
and the Japan Meteorological Agency Seismic Network~(JP) (Fig.~\ref{fig:source_correction}b).
The number of stations used for CMT inversion usually ranges
from~150 to~500.

To determine the source parameters in the starting model,
we used the CMT inversion algorithm of \cite{liu2004spectral}.
This algorithm combines a normalized waveform difference misfit with an envelope difference misfit.
Specifically, the algorithm minimizes the misfit function
\begin{equation}
   \begin{split}
      \Phi =  \sum\limits_{c=1}^{C} \omega_c \sum\limits_{r=1}^{R_c} \omega_{cr}
       \sum\limits_{w=1}^{W_{cr}} \omega_{crw}\,
          & \left\{ \lambda\, \frac
              { \int \big[ d_w(t) - s_w(t - \Delta t) \big]^2 \mathrm{d}t}
              {\int \big[ d_w(t) \big]^2  \mathrm{d}t} \right.
       \\ & \quad \left. \mbox{} + (1 - \lambda)\, \frac
              {\int \big[ e(d_w(t)) - e(s_w(t - \Delta t)) \big]^2 \mathrm{d}t}
              {\int \big[ e(d_w(t)) \big]^2\mathrm{d}t} \right\}
              \quad ,
   \end{split}
\end{equation}
where~$d_w(t)$ denotes data in time window~$w$\,,
and~$s_w(t - \Delta t)$ the corresponding synthetic for model~GLAD-M15.
We allow the synthetics to shift relative to the data by an amount~$\Delta t$
--- effectively a station correction --- determined by cross correlation.
The envelope function is denoted by~$e(\,\cdot\,)$\,,
and the parameter~$\lambda$ determines the balance between fitting waveforms versus fitting envelopes.
The number of measurement categories is denoted by~$C$\,.
Following~\cite{ekstrom2012global},
seismograms were filtered between 50~s and 100~s
to select three-component body-wave windows,
and between 60~s and 100~s to select three-component
surface-wave windows,
resulting in six measurement categories, $c=1,\ldots,C$\,.
To balance their contributions,
each category is weighted by the reciprocal of the number of measurements in that
category, $\omega_c$\,.
The number of windows for a given receiver~$r$ in a given measurement category~$c$ is~$W_{cr}$\,.
Each such window is weighted equally, i.e.,~$\omega_{crw}=1$\,.
The number of receivers that records data in category~$c$ is denoted by~$R_c$\,.
As shown in Fig.~\ref{fig:source_correction}b,
the receivers are unevenly distributed across the globe,
with several dense arrays in the Northern Hemisphere and poor coverage in the Southern Hemisphere.
To balance the coverage,
we assign receiver weights~$\omega_{cr}$ based on the expression
\begin{equation}
\omega_{cr}^{-1} = N_c\,\sum_{r'=1}^{R_c} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_c}\right)^2\right]
\quad ,
\label{eq:spatial_weights}
\end{equation}
{\color{Red} Wenjie: is it $\omega_{cr}^{-2}$ or $\omega_{cr}^{-1}$? And does the normalization factor~$N_c$ depend on~$c$?\\ }
where~$N_c$ is a normalization factor,
and where~$\Delta_{rr'}$ denotes the angular distance between receivers~$r$ and~$r'$\,.
The reference angular distance~$\Delta_c$ needs to be chosen such that the condition 
number of the diagonal weighting matrix defined by Eqn.~(\ref{eq:spatial_weights}) is not too large.
The calculation of the weights may be abstracted as: given a spatial distribution of
points on the unit sphere, determine a weighting associated with each point.

The algorithm inverts for the six elements of the moment tensor
and the centroid location~(latitude, longitude, and depth).
The calculation of each associated Fr\'echet derivative requires one full 3D forward simulation,
so, considering we have more than one thousand events,
these source inversions are computationally very expensive.

Because we allow the synthetics to shift by an amount~$\Delta t$ relative to the data,
the CMT inversion has unreliable sensitivity to the centroid time.
To alleviate this problem,
following~\cite{zhu2012structure},
we perform a subsequent grid search for the centroid time and the scalar moment.
The grid-search calibration involves simple shift and multiply operations on seismograms
and, unlike the CMT inversion, requires minimal simulation time.

Most earthquakes show a shallower depth after inversion
(Fig.~\ref{fig:source_correction}c),
consistent with our previous experiences~\citep[e.g.,][]{zhu2015seismic,chen2015multiparameter,bozdaug2016global} and with experiments by~\cite{hjorleifsdottir2010effects}.
We observed an average depth change of~$-2.62\pm2.49$~km relative to the global CMT solutions,
an average scalar moment change of~$5.31\pm3.91$\%,
and an average centroid time shift of~$-0.60\pm1.17$~s.
These are relatively minor corrections, especially in view of the significant expense of the source inversions.
For this reason, when we added another 440 earthquakes during iteration~22,
thereby bringing the total to~1,480 events,
we only performed a grid search to calibrate the centroid times and scalar moments.
Fig.~\ref{fig:event_1480} summarizes the characteristics of all 1,480 earthquakes used in this study.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/events_1480.pdf}
  \caption{1,480 earthquakes used in this study. (a) Distribution of earthquakes. The color of each beach ball reflects its depth range, where blue designate events shallower than 50~km, green events between 50~km and 300~km, and red events deeper than 300~km. (b) and (c) Histograms of earthquake moment magnitudes and depths.}
  \label{fig:event_1480}
\end{figure}

\section{Seismic data}
\label{section:data}

The seismographic stations used in this study were carefully selected to ensure global coverage and high data quality (Fig.~\ref{fig:stations}).
In addition to the seismic stations used for the source inversions,
we included all available data for our 1,480 event earthquake database from many data centers,
including IRIS, ORFEUS, INGV, IPGP, ETH, and GEONET.
Regional and temporary networks,
such as US Array~(TA),
Africa Array~(AF), the Canadian National Seismograph Network~(CN), Geoscience Australia~(AU),
the Antarctic Seismographic Argentinean Italian Network~(AI),
and the New Zealand National Seismograph Network~(NZ),
constitute a significant part
of our database and greatly improve coverage in certain regions.

\begin{figure}
  \includegraphics[width=0.8\textwidth]{figures/station_map.pdf}
  \caption{Distribution of 11,800 seismographic stations used in this study. Colors denote the number of events for which a given station contributes waveforms to the structural inversion. Stations with a number of event responses $<400$ are plotted in smaller size; these are usually temporary arrays deployed over a short period of time, frequently ocean bottom seismometers. The maximum number of event responses comes from ANMO, in Albuquerque, New Mexico, which contributed to 1,442 out of 1,480 earthquakes in the data set.}
  \label{fig:stations}
  \centering
\end{figure}

\subsection{Adaptable Seismic Data Format}
\label{section:ASDF}

Conventional seismic data formats, such as SAC, involve one file per time series plus related files with instrument response and event information.
Since every earthquake in the database is typically recorded by thousands of instruments, I/O during the preprocessing stage of the adjoint tomography workflow quickly cripples the file system.
The Adaptable Seismic Data Format (ASDF)~\citep[][ \texttt{https://seismic-data.org/ }]{krischer2016adaptable} was developed with complete reproducibility and fast parallel processing in mind.

In this context, there are four key issues ASDF resolves.
\begin{itemize}
    \item Robustness and stability: the data container is developed and maintained to ensure accuracy of scientific results.
    \item Data organization: the container is self-describing. Data, including waveform, source, and station information, are organized into well-defined structures.
    \item Reproducibility: the container enables scientists to keep track of what has been done to data so that results can be reproduced.
    \item Efficiency: the format provides easy mechanisms for parallel processing.
\end{itemize}
ASDF serves as a self-contained-and-explained data container while taking full advantages of parallel computing.
In our workflow,
one ASDF file contains all the information needed for data processing, including the seismic traces, event information files, and station response files.
The related APIs are carefully designed for easy data extraction and parallel implementation.

\section{Misfit function}
\label{section:misfit}

The misfit function to be minimized during the iterative inversion process must be carefully constructed.
It will typically involve cross-correlation traveltimes for body waves and frequency-dependent multitaper phase measurements for surface waves.
Measurements are made in several passbands of three-component seismograms rotated into vertical, radial, and transverse components, resulting in a number of measurement categories.
In this study, we consider four passbands,
namely, a 17--40~s passband targeting body waves,
two 40--100~s passbands separately targeting body and surface waves,
and a 90--250~s passband targeting longer-period surface waves.
Each passband involves measurements on all three components,
which results in a total of twelve measurement categories.
Although the inversion is designed to minimize the overall misfit,
we will be tracking the misfit reduction in each of the categories to ensure that the model is improving the fit to the data roughly equally across the board.
One of the biggest challenges in the construction of the misfit function is the highly uneven distribution of earthquakes and seismographic stations,
which must be counterbalanced by geographically weighting the data.
This issue is discussed in detail by~\cite{Ruanetal2018};
in this section we present a brief synopsis.

With these considerations in mind,
the overall misfit, $\Phi$, is defined as follows:
\begin{equation}
\label{eq:misfit}
\Phi = \sum_{s}^{S} \omega_s \sum_{c}^{C} \omega_{c} \sum_{r}^{R_{sc}} \omega_{scr} \sum_{w}^{W_{scr}} \omega_{scrw}\, \chi_{scrw}
\quad ,
\end{equation}
where~$S$ denotes the number of sources, $C$ the number of categories,
$R_{sc}$ the number of receivers recording source~$s$ in category~$c$,
and~$W_{scr}$ the number of measurement windows for source~$s$, category~$c$
and receiver~$r$.
The misfit for a specific source~$s$, category~$c$, receiver~$r$, and window~$w$ is
\begin{equation}
  \chi_{scrw} = \frac{1}{\Delta\omega}\int_{\omega_1}^{\omega_2} \Big( \frac {\Delta \tau_{scrw}} {\sigma_{scrw}} \Big)^2\, \mathrm{d}\omega
\quad ,
\end{equation}
where~$\Delta \tau_{scrw}$ denotes a multi-taper frequency-dependent phase measurement over the frequency interval~$\Delta\omega=\omega_2-\omega_1$\,,
with associated standard deviation~$\sigma_{scrw}$\,.
For body waves, the window misfit is simply the cross-correlation traveltime anomaly,
$\Delta T_{scrw}$\,, weighted by its standard deviation, i.e., $\chi_{scrw}=(\Delta T_{scrw}/\sigma_{scrw})^2$\,.
As in the source inversions,
the window weights are equal, $\omega_{scrw}=1$\,,
and the category weight, $\omega_c$\,, is the reciprocal of the number of measurements in that
category.
Earthquakes are mainly confined to plate boundaries,
and most seismic stations are confined to the continents,
which leads to a very uneven distribution of sources and stations,
as illustrated in Figs.~\ref{fig:event_1480} and~\ref{fig:stations}.
Therefore, weighting is crucial in global tomography to balance this uneven sampling
of Earth's interior.
Our source and receiver weighting strategy,
encapsulated by the weights~$\omega_s$ and $\omega_{scr}$\,,
is developed to compensate for uneven spatial sampling.
Following the same strategy as for the receiver weights in the source inversions,
we define the source and receiver weights as
\begin{equation}
\omega_{s}^{-1} = N\,\sum_{s'=1}^{S} \exp\left[\mbox{}-\left(\frac{\Delta_{ss'}}{\Delta}\right)^2\right]
\quad ,
\label{eq:source_weights}
\end{equation}
and
\begin{equation}
\omega_{scr}^{-1} = N_{sc}\,\sum_{r'=1}^{R_{sc}} \exp\left[\mbox{}-\left(\frac{\Delta_{rr'}}{\Delta_{sc}}\right)^2\right]
\quad ,
\label{eq:receiver_weights}
\end{equation}
respectively.
Here~$N$ and~$N_{sc}$ are a normalization factors,
and~$\Delta_{ss'}$ and~$\Delta_{rr'}$ denote angular distances between source and receiver pairs~$\{s,s'\}$ and~$\{r,r'\}$\,.
The reference angular distances~$\Delta$ and~$\Delta_{sc}$ need to be chosen based on the condition 
numbers of the diagonal weighting matrices defined by Eqns.~(\ref{eq:source_weights}) and~(\ref{eq:receiver_weights}).

{\color{red} Wenjie: is there just one $\Delta$, or are there different ones for sources, receivers and categories? And is there just one normalization constant~$N$, or are there multiple ones?}

\section{Model parametrization}

We use the same transversely isotropic model parametrization as starting model GLAD-M15.
Such a model is described by the five Love parameters $A$, $C$, $L$, $N$, and $F$~\citep{Love27},
or, alternatively, using the mass density~$\rho$, in terms of the wavespeeds~$\alpha_v=\sqrt{C/\rho}$, $\alpha_h=\sqrt{A/\rho}$, $\beta_v=\sqrt{L/\rho}$, $\beta_h=\sqrt{N/\rho}$ and the dimensionless parameter $\eta=F/(A-2L)$~\citep{PREM,DT98}.
Assuming the radial anisotropy is due to shear anisotropy, these five parameters
may be further reduced to four by introducing the bulk sound speed,
$c=\sqrt{\kappa/\rho}$\,.
Therefore, the final four parameters are $c$, $\beta_v$, $\beta_h$, and $\eta$.

Since density is difficult to constrain with seismic data,
density perturbations are scaled to isotropic (Voigt averaged) shear wavespeed perturbations based on the relationship~$\delta\ln\rho = 0.33\,\delta\ln\beta$~\citep{montagner1989petrological}.

Based on this parametrization,
the variation in the misfit function~(\ref{eq:misfit}) may be expressed as~\citep{zhu2015seismic,bozdaug2016global}
\begin{equation}
    \delta \Phi = \int_V
      (\delta \ln c\,K_c + \delta \ln\beta_v\,K_{\beta_v} + \delta \ln\beta_h\,K_{\beta_h} +
      \delta\ln\eta\,K_\eta) \mathrm{d}V
      \quad ,
\end{equation}
where~$K_c$, $K_{\beta_v}$, $K_{\beta_h}$, and $K_\eta$ denote the four Fr\'echet derivatives,
which are calculated based on an adjoint-state method~\citep[e.g.,][]{Plessix_2006_RAS,Tromp2005}.

\section{Adjoint tomography workflow}

The adjoint tomography workflow is shown in Fig.~\ref{fig:adjoint_workflow}.
It starts with the selection of earthquakes, as discussed in Section~\ref{section:earthquakes}.
Given the earthquake selection,
observed seismographic data and related response information are acquired,
as discussed in Section~\ref{section:data}.
For a given earthquake,
the corresponding seismograms and related response information are combined in a single ASDF file,
described in Section~\ref{section:ASDF}.
For a given earthquake dataset, the conversion to ASDF needs to be performed once and for all.
In the following sections we highlight several important aspects of the workflow.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/adjoint_workflow_6.pdf}
  \caption{Adjoint tomography workflow.}
  \label{fig:adjoint_workflow}
\end{figure}

\subsection{Forward simulations}

The observed seismograms need to be compared to corresponding synthetic seismograms
for the purpose of making measurements.
The forward simulations are based on the global spectral-element solver SPECFEM3D\_GLOBE~\citep{KoTr02a,KoTr02a},
and take a CMT solution, a relevant list of stations, and the current earth model as input.
The solver is GPU accelerated, and the simulations are performed on the Cray `Titan' at the Oak Ridge Leadership Computing Facility.
To simulate 120~min seismograms with a shortest period of 17~s on 384 NVIDIA Tesla K20X GPUs takes approximately 10~min of wall clock time.
The calculation of Fr\'echet derivatives at a later stage of the workflow requires access to snapshots of the forward wavefield as part of the parsimonious storage algorithm developed by~\cite{KoXiBoPeSaLiTr16},
with rapid I/O facilitated by ADIOS~\citep{liu2014hello}.
For the current simulation setup,
this requires about 1~TB of storage per earthquake,
so for 1,480 earthquakes this amounts to 1.5~PB of storage.

\subsection{Seismic data processing}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/Preprocess_workflow.pdf}
  \caption{Preprocessing workflow for seismic data.}
  \label{fig:preprocess_workflow}
\end{figure}
